---
title: "index"
output: html_document
---
#Summary Information file
```{r,echo=FALSE,message=FALSE}
library(dplyr)
library(plotly)
library(knitr)

data <- read.csv('data/intro_survey_data.csv', stringsAsFactors = FALSE)

source('scripts/summary_info.r')
info <- info_function(data)
```
This is a summary of the survey of the INFO 498 FC class that was filled out in the beginning of the quarter. There were a total of `r info$numOfResponse` and among them, there were: `r info$numOfFreshman` freshmen, `r info$numOfSophomore` sophomores, `r info$numOfJunior` juniors, and `r info$numOfSenior` seniors. Of the class, `r info$numofWindows` students use Windows as their primary OS, while `r info$numOfMac` students use Mac

Below is a table that shows how many students are looking to apply to the Informatics major for each class
`r kable(info$GradeApplyToInfo, format = 'markdown')`
According to the table, 13 freshmen, 36 sophomores, 15 juniors, and 3 seniors are looking to apply to the Informatic major

##More Interesting Data
Below is a table that shows how many students use a particular OS and are planning to apply to the major
`r kable(info$OSApplyToInfo, format = 'markdown')`
According to the table, 1 student uses Linux, 29 students use Mac, 1 student uses a combination of Windows at home and Linux (Ubuntu) at work, and 36 students use Windows

#Chart 1
Below is a chart that shows the number of students that are familiar with GitHub
```{r,echo=FALSE,message=FALSE}
source('scripts/chart_1.r')
build_chart_1(data)
```

#Chart 2
Below is a graph that shows INFO 498's programming experience for the students in the class
```{r,echo=FALSE,message=FALSE}
source('scripts/chart2.r')
make_chart_2(data)
```
